MRD_final_microbiome

### 2019-06-28 import_popln_data.Rmd
updated

mnd.i.melt = melt(mnd.i, id = 'Location')
mnd.i.melt$variable <- as.numeric.factor(mnd.i.melt$variable)
ggplot(mnd.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="mnd Incidence") + 
  xlab("Year")

mnd.p.melt = melt(mnd.i, id = 'Location')
mnd.p.melt$variable <- as.numeric.factor(mnd.p.melt$variable)
ggplot(mnd.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="mnd Prevalance") + 
  xlab("Year")

ipd.i.melt = melt(ipd.i, id = 'Location')
ipd.i.melt$variable <- as.numeric.factor(ipd.i.melt$variable)
ggplot(ipd.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="ipd Incidence") + 
  xlab("Year")

ipd.p.melt = melt(ipd.i, id = 'Location')
ipd.p.melt$variable <- as.numeric.factor(ipd.p.melt$variable)
ggplot(ipd.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="ipd Prevalance") + 
  xlab("Year")

ad.i.melt = melt(ad.i, id = 'Location')
ad.i.melt$variable <- as.numeric.factor(ad.i.melt$variable)
ggplot(ad.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="AD Incidence") + 
  xlab("Year")

ad.p.melt = melt(ad.i, id = 'Location')
ad.p.melt$variable <- as.numeric.factor(ad.p.melt$variable)
ggplot(ad.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="AD Prevalance") + 
  xlab("Year")

>>>>

require(cowplot)
theme_set(theme_cowplot(font_size=12)) # reduce default font size

mnd.i.melt = melt(mnd.i, id = 'Location')
mnd.i.melt$variable <- as.numeric.factor(mnd.i.melt$variable)
p1 <- ggplot(mnd.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="mnd Incidence") + 
  xlab("Year") + theme(legend.position="none")

mnd.p.melt = melt(mnd.i, id = 'Location')
mnd.p.melt$variable <- as.numeric.factor(mnd.p.melt$variable)
p2 <-  ggplot(mnd.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="mnd Prevalance") + 
  xlab("Year") + theme(legend.position="none")

ipd.i.melt = melt(ipd.i, id = 'Location')
ipd.i.melt$variable <- as.numeric.factor(ipd.i.melt$variable)
p3 <- ggplot(ipd.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="ipd Incidence") + 
  xlab("Year") + theme(legend.position="none")

ipd.p.melt = melt(ipd.i, id = 'Location')
ipd.p.melt$variable <- as.numeric.factor(ipd.p.melt$variable)
p4 <-  ggplot(ipd.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="ipd Prevalance") + 
  xlab("Year") + theme(legend.position="none")

ad.i.melt = melt(ad.i, id = 'Location')
ad.i.melt$variable <- as.numeric.factor(ad.i.melt$variable)
p5 <-  ggplot(ad.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="AD Incidence") + 
  xlab("Year") + theme(legend.position="none")

ad.p.melt = melt(ad.i, id = 'Location')
ad.p.melt$variable <- as.numeric.factor(ad.p.melt$variable)
p6 <- ggplot(ad.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="AD Prevalance") + 
  xlab("Year") + theme(legend.position="none")

final <- plot_grid(p1, p2,p3,p4,p5,p6, labels = c('A', 'B','C', 'D','E', 'F'),ncol = 2)
ggsave("overview.jpg", final) 
```
